---
title: "Opportunistic Exploration — Replication Data"
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    theme: united
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: false
    code_folding: hide
    code_download: true
---

```{css, echo=FALSE}
body {
  font-size: 1.6rem;
  text-align: justify;
}

.title {
  font-size: 47px;
  color: firebrick;
}

h1,h2,h3,h4,h5 {
  text-align: left;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)

rerun_fit_models <<- "no"

source(here::here("Analysis", "main_task", "packages.R"))
library(patchwork)
source(here::here("Analysis", "main_task", "fit.R"))
source(here::here("Analysis", "main_task", "plotting_funcs.R"))


# first, let's compile a df of the participants whose data passes
# our exclusion criteria; note that unlike the `free_choices.csv` file,
# which also prunes participants who fail to meet the exclusion
# criteria, this df keeps forced choices, too; keeping these forced choice
# trials will be useful for analyzing whether participants took massive breaks
# between any trials

preprocessed_df <- read_parquet(here("Data", "Main_Task", "preprocessed_df.parquet"))
free_choice_df <<- read_csv(here("Data", "Main_Task", "free_choices.csv"))

subids_with_enough_trials <- preprocessed_df %>%
  group_by(batch) %>%
  count(subid) %>%
  slice_max(n) %>%
  pull(subid)


preprocessed_df_usable_participants_full_data_set <- preprocessed_df %>%
  filter(
    subid %in% subids_with_enough_trials,
    q1 == "Not at all",
    q2 == "Not at all",
    q3 == "Always",
    sub_avg_accuracy > .8
  )

participants_by_experiment_duration <-
  preprocessed_df_usable_participants_full_data_set %>% 
  filter(forced_choice == 0) %>%
  group_by(subid, batch) %>%
  summarise(
    max_time_elapsed = max(time_elapsed_main_exp) / 60000,
    median_choice_time = median(choice_time) / 1000
  )

trials_following_massive_delays <- 
preprocessed_df %>%
    filter(
        subid %in% subids_with_enough_trials,
        q1 == "Not at all",
        q2 == "Not at all",
        q3 == "Always",
        sub_avg_accuracy > .8
    ) %>%
    group_by(subid, forced_choice) %>%
    mutate(perc_mult = if_else(forced_choice == 1, NA_real_, mean(selection == "mult"))) %>%
    group_by(subid) %>%
    mutate(perc_mult = mean(perc_mult, na.rm = T)) %>%
    filter(
        between(perc_mult, .15, .85)
    ) %>%
    ungroup() %>%
    mutate(choice_time = choice_time / (60 * 1000)) %>%
    filter(choice_time > 20) %>%
    select(subid, game_nr, trial_nr, batch, choice_time) %>%
    arrange(subid, choice_time)

pcpts_taking_massive_delays <- trials_following_massive_delays %>%
  pull(subid) %>%
  unique

custom_compare_paired_fits <- function(pair_compairison, coef_of_interest, keep_batch,
                                keep_separate_by_exposure,
                                keep_iv, keep_aggregation, keep_continuum,
                                group_1, group_2, group_1_exposure,
                                group_2_exposure, min_duration, max_duration,
                                type_of_test, run_test = T,
                                pcpts_to_exclude = c()){
  
  paired_fits <- load_paired_fits(
    keep_batch, keep_separate_by_exposure, keep_iv,
    keep_aggregation, keep_continuum, group_1, group_2, group_1_exposure,
    group_2_exposure
  ) %>%
    filter(!subid %in% pcpts_to_exclude) %>%
    arrange(subid, free_choice_label) %>%
    left_join(participants_by_experiment_duration) %>%
    filter(max_time_elapsed >= min_duration, max_time_elapsed <= max_duration)
  
  n_participants <- n_distinct(paired_fits$subid)
  
  if (run_test){
    exec(
      type_of_test,
      paired_fits %>%
        filter(free_choice_label == group_1) %>%
        pull(!!coef_of_interest),
      paired_fits %>%
        filter(free_choice_label == group_2) %>%
        pull(!!coef_of_interest),
      paired = T,
      alternative = pair_compairison
    ) %>%
      broom::tidy() %>%
      mutate(num_participants = n_participants)
  } else{
    pivot_wider(
      paired_fits,
      id = c(
        batch, subid, free_choice_trial, equal_exposure, separate_by_exposure,
        iv, aggregation, continuum, max_time_elapsed, median_choice_time
      ),
      names_from = horizon_type,
      values_from = c(
        horizon, free_choice_label, total_mult_chosen, total_trials, data, 
        temp_coef, difficulty_coef, side_coef, information_coef
      )
    )
  }

}

```

### The model we are using to fit the data


$$
p_{mult} = \frac{1}{1 + exp(\frac{R_{mult} - R_{add} + \alpha(I_{mult} - I_{add}) + D(M_{add} - M_{mult}) + B}{\sqrt2\sigma})}
$$

### Are the coefficients significantly different between the short and long horizons?
```{r main_test_of_coefficients}

map2_dfr(
  c("greater", "less", "less"),
  c("difficulty", "information", "temp"),
  ~custom_compare_paired_fits(
  .x, paste0(.y, "_coef"), "replication", F, "rt", "percentile",
  "continuous", "Short horizon, free choice 1", "Long horizon, free choice 1",
  F, F, 0, Inf, "t.test"
  ) %>%
    mutate(coefficient = .y) %>%
    select(coefficient, estimate, statistic, p.value)
)

```

### Coefficient estimates for long vs. short horizons for exploratory and replication data

```{r visualize coefficients, fig.width=10, fig.height=15}


map(
  c("difficulty", "information", "temp"),
  ~{
    
    my_aggregation = "percentile"
    my_coef = paste0(.x, "_coef")
    my_iv = "rt"

exploratory_short <- here("Analysis", "main_task", "fits.rds") %>%
  read_rds() %>%
  filter(
    batch == "exploratory",
    separate_by_exposure == F,
    iv == my_iv,
    aggregation == my_aggregation,
    continuum == "continuous",
    (free_choice_label == "Short horizon, free choice 1" & equal_exposure == F) |
      (free_choice_label == "Long horizon, free choice 1" & equal_exposure == F)
  ) %>%
  group_by(subid) %>%
  filter(
    min(total_mult_chosen) >= 3,
    max(total_trials - total_mult_chosen) >= 3
  ) %>%
  ungroup() %>%
  mutate(across(c(free_choice_trial), as_factor)) %>%
  arrange(subid, free_choice_label) %>%
  filter(free_choice_label == "Short horizon, free choice 1") %>%
  pull(!!my_coef)

exploratory_long <- here("Analysis", "main_task", "fits.rds") %>%
  read_rds() %>%
  filter(
    batch == "exploratory",
    separate_by_exposure == F,
    iv == my_iv,
    aggregation == my_aggregation,
    continuum == "continuous",
    (free_choice_label == "Short horizon, free choice 1" & equal_exposure == F) |
      (free_choice_label == "Long horizon, free choice 1" & equal_exposure == F)
  ) %>%
  group_by(subid) %>%
  filter(
    min(total_mult_chosen) >= 3,
    max(total_trials - total_mult_chosen) >= 3
  ) %>%
  ungroup() %>%
  mutate(across(c(free_choice_trial), as_factor)) %>%
  arrange(subid, free_choice_label) %>%
  filter(free_choice_label == "Long horizon, free choice 1") %>%
  pull(!!my_coef)

replication_short <- here("Analysis", "main_task", "fits.rds") %>%
  read_rds() %>%
  filter(
    batch == "replication",
    separate_by_exposure == F,
    iv == my_iv,
    aggregation == my_aggregation,
    continuum == "continuous",
    (free_choice_label == "Short horizon, free choice 1" & equal_exposure == F) |
      (free_choice_label == "Long horizon, free choice 1" & equal_exposure == F)
  ) %>%
  group_by(subid) %>%
  filter(
    min(total_mult_chosen) >= 3,
    max(total_trials - total_mult_chosen) >= 3
  ) %>%
  ungroup() %>%
  mutate(across(c(free_choice_trial), as_factor)) %>%
  arrange(subid, free_choice_label) %>%
  filter(free_choice_label == "Short horizon, free choice 1") %>%
  pull(!!my_coef)


replication_long <- here("Analysis", "main_task", "fits.rds") %>%
  read_rds() %>%
  filter(
    batch == "replication",
    separate_by_exposure == F,
    iv == my_iv,
    aggregation == my_aggregation,
    continuum == "continuous",
    (free_choice_label == "Short horizon, free choice 1" & equal_exposure == F) |
      (free_choice_label == "Long horizon, free choice 1" & equal_exposure == F)
  ) %>%
  group_by(subid) %>%
  filter(
    min(total_mult_chosen) >= 3,
    max(total_trials - total_mult_chosen) >= 3
  ) %>%
  ungroup() %>%
  mutate(across(c(free_choice_trial), as_factor)) %>%
  arrange(subid, free_choice_label) %>%
  filter(free_choice_label == "Long horizon, free choice 1") %>%
  pull(!!my_coef)


bind_rows(
  tibble(
    x = "exploratory_short",
    y = exploratory_short
  ),
  
  tibble(
    x = "exploratory_long",
    y = exploratory_long
  ),
  
  tibble(
    x = "replication_short",
    y = replication_short
  ),
  
  tibble(
    x = "replication_long",
    y = replication_long
  )
) %>%
  ggplot(aes(x = x, y = y)) +
  geom_violin() +
  geom_jitter(width =.1) +
  geom_boxplot(width = .1, outlier.shape = NA) +
  theme(legend.position = "none") +
  labs(
    title = .x,
    x = "",
    y = "Coefficent Estimate per Participant"
  )
  }
) %>%
  reduce(`/`)


```



```{r, analysis_combos_df, rows.print=50}

analysis_combos <- expand.grid(
  pair_compairison = c("greater", "less"),
  coef_of_interest = c("difficulty_coef", "information_coef", "temp_coef"),
  keep_batch = c("exploratory", "replication"),
  keep_separate_by_exposure = F,
  keep_iv = c("rt", "difficulty"),
  keep_aggregation = c("raw", "percentile"),
  keep_continuum = "continuous",
  group_1 = "Short horizon, free choice 1",
  group_2 = "Long horizon, free choice 1",
  min_duration = c(0),
  max_duration = c(Inf),
  type_of_test = c("t.test", "wilcox.test")
) %>%
  mutate(
    group_1_exposure = keep_separate_by_exposure,
    group_2_exposure = keep_separate_by_exposure
  ) %>%
  filter(max_duration > min_duration) %>%
  filter(
    (coef_of_interest == "difficulty_coef" &  pair_compairison == "greater") |
      coef_of_interest != "difficulty_coef" & pair_compairison == "less") %>%
  relocate(type_of_test, .after = last_col()) %>%
  mutate(across(where(is.factor), as.character))

map_dfr(1:nrow(analysis_combos), ~{
  arow <- analysis_combos %>% filter(row_number() == .x)
  
  brow <- custom_compare_paired_fits(
    arow$pair_compairison, arow$coef_of_interest, arow$keep_batch,
    arow$keep_separate_by_exposure, arow$keep_iv, arow$keep_aggregation,
    arow$keep_continuum, arow$group_1, arow$group_2, arow$group_1_exposure,
    arow$group_2_exposure, arow$min_duration, arow$max_duration,
    arow$type_of_test
  )
  
  bind_cols(arow, brow)
  
}) %>%
  arrange(coef_of_interest, keep_batch, -p.value) %>%
  mutate(across(p.value, ~insight::format_p(.x))) %>%
  select(coef_of_interest, keep_batch, p.value, keep_iv, keep_aggregation, type_of_test) %>%
  rename_with(~str_replace_all(.x, "keep_", " "), starts_with("keep_"))

```


## Maybe we should be more vigilant of how long tasks are taking participants?

### It doesn't appear that participants who finish the task quickly are particularly driving the null results (i.e., their coefficient isn't particulaly large).
```{r, fig.width=10, fig.height=15}

map(
    c("max_time_elapsed", "median_choice_time"),
    function(desired_x_axis){
        map(c("exploratory", "replication"), ~
                custom_compare_paired_fits(
                    "greater", "difficulty_coef", .x, F, "rt", "percentile",
                    "continuous", "Short horizon, free choice 1", "Long horizon, free choice 1",
                    F, F, 0, Inf, "t.test", F
                ) %>%
                mutate(difficulty_coef_diff = difficulty_coef_Long - difficulty_coef_Short) %>%
                filter(max_time_elapsed < 100) %>%
                ggplot(aes(!!sym(desired_x_axis), difficulty_coef_diff)) +
                geom_smooth() +
                geom_point() +
                labs(
                    title = paste(
                        .x,
                        "batch,",
                        ifelse(
                            desired_x_axis == "max_time_elapsed",
                            "experiment duration (including instrc)",
                            "average free choice RT"
                        )
                        ),
                    x = ifelse(
                            desired_x_axis == "max_time_elapsed",
                            "Minutes taken to go through entire task",
                            "Average time to make a free choice (in seconds)"
                        ),
                    y = "Difficulty Coefficient"
                )
        ) %>%
            reduce(`/`)
    }
) %>% reduce(`|`)


```


### Average amount of time spent on a free choice, over the course of the task (excluding 32 trials that lasted longer than 2 minutes)
```{r task_quickness_over_course_of_experiment}

free_choice_df %>%
  mutate(choice_time = choice_time / (60 * 1000)) %>%
  filter(choice_time < 2) %>%
  ggplot(aes(overall_trial, choice_time)) +
  geom_smooth()

```


### Some participants took a massive amount of time (breaks) to complete some of the trials
```{r long_breaks, rows.print=50}

trials_following_massive_delays
```

### But modeling the results without these participants doesn't make our results any more significant

```{r results_arent_better_if_we_discard_participants_who_break}

custom_compare_paired_fits(
                    "greater", "difficulty_coef", "replication", F, "rt", "percentile",
                    "continuous", "Short horizon, free choice 1", "Long horizon, free choice 1",
                    F, F, 0, Inf, "t.test", T, pcpts_taking_massive_delays
                ) %>%
  pull(p.value)
```

### However, if we keep the data from all participants and filter each of these participants by how far along they were in the task, the replication data look more promising

```{r adssa}

tribble(
  ~"First_x_Trials", ~"Exploratory", ~"Replication",
  20,                0.05671,        0.4849,
  40,                1.053e-05,      0.002351,
  60,                2.019e-05,      0.03906,
  80,                2.729e-07,      0.05509
)
```

## Choice Curves (for replication data)

### How much harder mult is than add side and likelihood of choosing mult

Difficulty is measured here by raw baseline RT

```{r fig.width=10}

input <- list()

input$batch_choice_curve <- "replication"   # "exploratory" "replication"
input$y_var_choice_curve <- "mult" # accuracy bigger_rand bigger_side bigger_rew_exposed_cum_mean bigger_rew_exposed_cum_count bigger_rew_latent bigger_rew_exposed_cum_sd
input$x_raw_or_percent <- "raw" # raw percent
input$choice_combos_choice_curve <- c("Long horizon, free choice 1", "Short horizon, free choice 1") # "Short horizon, free choice 1" "Long horizon, free choice 1"  "Long horizon, free choice 2"  "Long horizon, free choice 3"  "Long horizon, free choice 4"  "Long horizon, free choice 5"
input$x_comparison_group <- "mult" # rew_exposed_cum_sd rew_exposed_cum_mean rew_latent side rand
input$x_comparison_dimension <- "rt" # rew_exposed_cum_mean rew_latent difficulty rand rew_exposed_cum_sd
input$show_CI_choice_curve <- T # F

choice_and_learning_plots("choice_curve")
```

Difficulty is measured here by raw baseline self-rated difficulty

```{r fig.width=10}

input$batch_choice_curve <- "replication"   # "exploratory" "replication"
input$y_var_choice_curve <- "mult" # accuracy bigger_rand bigger_side bigger_rew_exposed_cum_mean bigger_rew_exposed_cum_count bigger_rew_latent bigger_rew_exposed_cum_sd
input$x_raw_or_percent <- "raw" # raw percent
input$choice_combos_choice_curve <- c("Long horizon, free choice 1", "Short horizon, free choice 1") # "Short horizon, free choice 1" "Long horizon, free choice 1"  "Long horizon, free choice 2"  "Long horizon, free choice 3"  "Long horizon, free choice 4"  "Long horizon, free choice 5"
input$x_comparison_group <- "mult" # rew_exposed_cum_sd rew_exposed_cum_mean rew_latent side rand
input$x_comparison_dimension <- "difficulty" # rew_exposed_cum_mean rew_latent difficulty rand rew_exposed_cum_sd
input$show_CI_choice_curve <- T # F

choice_and_learning_plots("choice_curve")
```


### Next two plots are same as previous two, except difficulty has been scaled between 1-100 rather than being in raw units

Difficulty is measured here by scaled baseline RT

```{r fig.width=10}

input$batch_choice_curve <- "replication"   # "exploratory" "replication"
input$y_var_choice_curve <- "mult" # accuracy bigger_rand bigger_side bigger_rew_exposed_cum_mean bigger_rew_exposed_cum_count bigger_rew_latent bigger_rew_exposed_cum_sd
input$x_raw_or_percent <- "percent" # raw percent
input$choice_combos_choice_curve <- c("Long horizon, free choice 1", "Short horizon, free choice 1") # "Short horizon, free choice 1" "Long horizon, free choice 1"  "Long horizon, free choice 2"  "Long horizon, free choice 3"  "Long horizon, free choice 4"  "Long horizon, free choice 5"
input$x_comparison_group <- "mult" # rew_exposed_cum_sd rew_exposed_cum_mean rew_latent side rand
input$x_comparison_dimension <- "rt" # rew_exposed_cum_mean rew_latent difficulty rand rew_exposed_cum_sd
input$show_CI_choice_curve <- T # F

choice_and_learning_plots("choice_curve")
```

Difficulty is measured here by scaled baseline self-rated difficulty

```{r fig.width=10}

input$batch_choice_curve <- "replication"   # "exploratory" "replication"
input$y_var_choice_curve <- "mult" # accuracy bigger_rand bigger_side bigger_rew_exposed_cum_mean bigger_rew_exposed_cum_count bigger_rew_latent bigger_rew_exposed_cum_sd
input$x_raw_or_percent <- "percent" # raw percent
input$choice_combos_choice_curve <- c("Long horizon, free choice 1", "Short horizon, free choice 1") # "Short horizon, free choice 1" "Long horizon, free choice 1"  "Long horizon, free choice 2"  "Long horizon, free choice 3"  "Long horizon, free choice 4"  "Long horizon, free choice 5"
input$x_comparison_group <- "mult" # rew_exposed_cum_sd rew_exposed_cum_mean rew_latent side rand
input$x_comparison_dimension <- "difficulty" # rew_exposed_cum_mean rew_latent difficulty rand rew_exposed_cum_sd
input$show_CI_choice_curve <- T # F

choice_and_learning_plots("choice_curve")
```


### Probability of choosing mult based on how much more or less rewarding (in points) it's been, compared to addition side

```{r fig.width=10}

input$batch_choice_curve <- "replication"   # "exploratory" "replication"
input$y_var_choice_curve <- "mult" # mult accuracy bigger_rand bigger_side bigger_rew_exposed_cum_mean bigger_rew_exposed_cum_count bigger_rew_latent bigger_rew_exposed_cum_sd
input$x_raw_or_percent <- "raw" # raw percent
input$choice_combos_choice_curve <- c("Long horizon, free choice 1", "Short horizon, free choice 1") # "Short horizon, free choice 1" "Long horizon, free choice 1"  "Long horizon, free choice 2"  "Long horizon, free choice 3"  "Long horizon, free choice 4"  "Long horizon, free choice 5"
input$x_comparison_group <- "mult" # mult rew_exposed_cum_sd rew_exposed_cum_mean rew_latent side rand
input$x_comparison_dimension <- "rew_exposed_cum_mean" # rt rew_exposed_cum_mean rew_latent difficulty rand rew_exposed_cum_sd
input$show_CI_choice_curve <- T # T F
choice_and_learning_plots("choice_curve")
```


## Choice Curves (for exploratory data)

### How much harder mult is than add side and likelihood of choosing mult

Difficulty is measured here by raw baseline RT

```{r fig.width=10}

input <- list()

input$batch_choice_curve <- "exploratory"   # "exploratory" "replication"
input$y_var_choice_curve <- "mult" # accuracy bigger_rand bigger_side bigger_rew_exposed_cum_mean bigger_rew_exposed_cum_count bigger_rew_latent bigger_rew_exposed_cum_sd
input$x_raw_or_percent <- "raw" # raw percent
input$choice_combos_choice_curve <- c("Long horizon, free choice 1", "Short horizon, free choice 1") # "Short horizon, free choice 1" "Long horizon, free choice 1"  "Long horizon, free choice 2"  "Long horizon, free choice 3"  "Long horizon, free choice 4"  "Long horizon, free choice 5"
input$x_comparison_group <- "mult" # rew_exposed_cum_sd rew_exposed_cum_mean rew_latent side rand
input$x_comparison_dimension <- "rt" # rew_exposed_cum_mean rew_latent difficulty rand rew_exposed_cum_sd
input$show_CI_choice_curve <- T # F

choice_and_learning_plots("choice_curve")
```

Difficulty is measured here by raw baseline self-rated difficulty

```{r fig.width=10}

input$batch_choice_curve <- "exploratory"   # "exploratory" "replication"
input$y_var_choice_curve <- "mult" # accuracy bigger_rand bigger_side bigger_rew_exposed_cum_mean bigger_rew_exposed_cum_count bigger_rew_latent bigger_rew_exposed_cum_sd
input$x_raw_or_percent <- "raw" # raw percent
input$choice_combos_choice_curve <- c("Long horizon, free choice 1", "Short horizon, free choice 1") # "Short horizon, free choice 1" "Long horizon, free choice 1"  "Long horizon, free choice 2"  "Long horizon, free choice 3"  "Long horizon, free choice 4"  "Long horizon, free choice 5"
input$x_comparison_group <- "mult" # rew_exposed_cum_sd rew_exposed_cum_mean rew_latent side rand
input$x_comparison_dimension <- "difficulty" # rew_exposed_cum_mean rew_latent difficulty rand rew_exposed_cum_sd
input$show_CI_choice_curve <- T # F

choice_and_learning_plots("choice_curve")
```


### Next two plots are same as previous two, except difficulty has been scaled between 1-100 rather than being in raw units

Difficulty is measured here by scaled baseline RT

```{r fig.width=10}

input$batch_choice_curve <- "exploratory"   # "exploratory" "replication"
input$y_var_choice_curve <- "mult" # accuracy bigger_rand bigger_side bigger_rew_exposed_cum_mean bigger_rew_exposed_cum_count bigger_rew_latent bigger_rew_exposed_cum_sd
input$x_raw_or_percent <- "percent" # raw percent
input$choice_combos_choice_curve <- c("Long horizon, free choice 1", "Short horizon, free choice 1") # "Short horizon, free choice 1" "Long horizon, free choice 1"  "Long horizon, free choice 2"  "Long horizon, free choice 3"  "Long horizon, free choice 4"  "Long horizon, free choice 5"
input$x_comparison_group <- "mult" # rew_exposed_cum_sd rew_exposed_cum_mean rew_latent side rand
input$x_comparison_dimension <- "rt" # rew_exposed_cum_mean rew_latent difficulty rand rew_exposed_cum_sd
input$show_CI_choice_curve <- T # F

choice_and_learning_plots("choice_curve")
```

Difficulty is measured here by scaled baseline self-rated difficulty

```{r fig.width=10}

input$batch_choice_curve <- "exploratory"   # "exploratory" "replication"
input$y_var_choice_curve <- "mult" # accuracy bigger_rand bigger_side bigger_rew_exposed_cum_mean bigger_rew_exposed_cum_count bigger_rew_latent bigger_rew_exposed_cum_sd
input$x_raw_or_percent <- "percent" # raw percent
input$choice_combos_choice_curve <- c("Long horizon, free choice 1", "Short horizon, free choice 1") # "Short horizon, free choice 1" "Long horizon, free choice 1"  "Long horizon, free choice 2"  "Long horizon, free choice 3"  "Long horizon, free choice 4"  "Long horizon, free choice 5"
input$x_comparison_group <- "mult" # rew_exposed_cum_sd rew_exposed_cum_mean rew_latent side rand
input$x_comparison_dimension <- "difficulty" # rew_exposed_cum_mean rew_latent difficulty rand rew_exposed_cum_sd
input$show_CI_choice_curve <- T # F

choice_and_learning_plots("choice_curve")
```


### Probability of choosing mult based on how much more or less rewarding (in points) it's been, compared to addition side

```{r fig.width=10}

input$batch_choice_curve <- "exploratory"   # "exploratory" "replication"
input$y_var_choice_curve <- "mult" # mult accuracy bigger_rand bigger_side bigger_rew_exposed_cum_mean bigger_rew_exposed_cum_count bigger_rew_latent bigger_rew_exposed_cum_sd
input$x_raw_or_percent <- "raw" # raw percent
input$choice_combos_choice_curve <- c("Long horizon, free choice 1", "Short horizon, free choice 1") # "Short horizon, free choice 1" "Long horizon, free choice 1"  "Long horizon, free choice 2"  "Long horizon, free choice 3"  "Long horizon, free choice 4"  "Long horizon, free choice 5"
input$x_comparison_group <- "mult" # mult rew_exposed_cum_sd rew_exposed_cum_mean rew_latent side rand
input$x_comparison_dimension <- "rew_exposed_cum_mean" # rt rew_exposed_cum_mean rew_latent difficulty rand rew_exposed_cum_sd
input$show_CI_choice_curve <- T # T F
choice_and_learning_plots("choice_curve")
```


